\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}). Therefore, with no lack of generality, the parameterised MR can be reduced to
\begin{displaymath}
    \text{MR} = \frc{\mu_{i}}{\mu_{j}},
\end{displaymath}
 i.e., the viscosity ratio. Fingering will occur in immiscible displacements when the viscosity ratio is greater than unity. As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers. The interface collapses and starts splitting into new lobes of fingers. One of the fingers may eventually outgrow the others and then spread to occupy an increasingly larger width. In the process, the finger reaches a width that is again unstable and splits again, and the pattern repeats itself. Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.

>>>>

From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}). Therefore, with no lack of generality, the MR can be reduced to
\begin{displaymath}
    \text{MR} = \frc{\mu_{i}}{\mu_{j}},
\end{displaymath}
 i.e., the viscosity ratio. Analysis performed in the following sections will make use of this simplified definition as phase saturation is a prognostic field that is calculated along with pressure and velocity. \red{(PARAGRAPH NEEDS TO BE IMPROVED)}

Viscous fingering occurs in immiscible displacements when the viscosity ratio is greater than unity. As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers. The interface collapses and starts splitting into new lobes of fingers. One of the fingers may eventually outgrow the others and then spread to occupy an increasingly larger width. In the process, the finger reaches a width that is again unstable and splits again, and the pattern repeats itself. Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
